Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-01 inst/paper/main.tex
use cases

\mypara{Record Current Call.}
R provides a \c{match.call} function which can return the current
call. This is heavily used by the statistical model-fitting functions
that records the current call that is then reevaluated in the
different environment. Another pattern is to match the current call,
adjust some arguments and pass it to another function. For example the
\c{write.csv} function changes the \c{sep} argument in the matched
call and reevaluates itself as \c{write.table}:
%
\begin{lstlisting}
    Call <- match.call(expand.dots = TRUE)
    Call$sep <- ","; Call[[1L]] <- as.name("write.table")
    eval.parent(Call)
\end{lstlisting}

@@

\subsection{Necessity of Eval}

>>>>

\mypara{Intercession.} A common use case for \eval is to be combined
with \c{match.call}. What \c{match.call} does is step up the call
stack and capture the invocation of the currently executing function
and return it as an unevaluated expression. The general pattern here
is that a call to some function \c{f} is transformed to a call to
another function \c{g} with some arguments retained and others
modified. An illustration taken from the \c{vcpart} package shows a
function \c{tvcglm} that is translated to the \c{tvcm} function but
with two modifications to the argument list, argument \c{control}
can't be missing and argument \c{fit} is forced to have value \c{glm}.
The function ends with a call to \c{eval.parent} to ensure that the
rewritten call is evaluted in the same environment the original call
was.
\begin{lstlisting}
 tvcglm <- function(formula, data, family, control=tvcglm_control(), ...) {
   Call <- match.call()
   Call[[1L]] <- as.name("tvcm")
   if (!"control" %in% names(Call)) Call$control<-formals(tvcglm)$control
   if ("fit" %in% names(list(...))) warning("'fit' is ignored. ")
   Call$fit <- "glm"
   return(eval.parent(Call))
 }
\end{lstlisting}

\mypara{Code Generation.} The more traditional use of \eval is to
execute code that was assembled by the programmer into a string. Here
we show the method \c{plot} for class \c{sback} in package
\c{wsbackfit}, simplified for explanatory purposes. The function takes
a long argument list, the names of which are captured in the list
\c{opt}. The string \c{stub} is composed of a subset of the arguments
passed to this function; the variable is used to construct a call to
\c{base::plot} which will draw a plot. \NOTE{This example is a bit
  messed up. What is var? Does the use of ... in the eval grab the
  arguments of this call? If yes does it not end up with xlab twice?
  HELP}
\begin{lstlisting}
 plot.sback <- function(x,...) {
   opt <- names(list(...))
   stub <- paste(
    ifelse("xlab" %in% opt,"",paste(",xlab=\"",var,"\"",sep="")),
    ifelse("main" %in% opt,"",main.aux),
    ifelse("type" %in% opt,"",",type=\"l\""),
    sep = "")
   plot <- paste("plot(x.data,",stub,",...)", sep = "")
   eval(parse(text=plot))
   ...
\end{lstlisting}

@@
